% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Baoyaun Geng}

\basicInfo{
  \email{gugegby@gmail.com} \textperiodcentered\ 
  \phone{(+86) 185-397-9675} \textperiodcentered\ 
  \github[d0ot]{https://github.com/D0ot}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{HeFei University of Technology (HFUT)}, Xuancheng, China}{2018 -- Present}
\textit{B.S.} in Computer Science (CS)


\section{\faUsers\ Experience and Projects}

\datedsubsection{\textbf{RoboCup Labtorary of HFUT}}{Apr. 2019 -- Present}
\role{Member}

The RoboCup Labtorary of HFUT mainly focus on RoboCup 3D Simulation.

\begin{itemize}
  \item Maintain Robocup3D develop environment installer.
  \item Using CMA-ES to optimize behaviors of agent(robot).
\end{itemize}

\datedsubsection{\textbf{ZGMOS Project}}{Apr.2021 -- Present}
\role{Contest project, colaborated with two classmates of mine: Peng Zou, Xiaoyang Ma}

This project is to implement a xv-6 like toy kernel running on RISC-V platform. it is still work in progress.

\begin{itemize}
  \item Multi-Threading / Context switch is implemented
  \item ELF Loader, it can load and run ELF executables
  \item A Read-Only FAT32 FS
  \item A Simple Virtual FileSystem
  \item Implement some syscalls
\end{itemize}

\datedsubsection{\textbf{GLEC2 Project}}{Jun.2021 -- Jul.2021}
\role{Individual project, also a Computer Architecture course design}

This project is to implement a RV32I CPU Core. 

\begin{itemize}
  \item Almost full RV32I ISA implementation, except for CSR and ECALL instructions.
  \item Classic 5 stages pipeline design.
  \item Configurable, data bypass and full stall implementation are also supported.
  \item Writen in SpinalHDL(a lib of Scala). A practice of agile development.
\end{itemize}

\datedsubsection{\textbf{Other Projects}}{}
\role{All are individual projects}

These project could be fun or useful.

\begin{itemize}
  \item GLEC, a single cycle RV32I CPU Core.
  \item Robocup3dInstaller, the Robocup3D develop environment installer.
  \item gb\_onenotehelper, An AHK script to enhance device with signle button Stylus-Pen 
  \item subw2r, A command line tool to generate v2ray config file from a subscription link
\end{itemize}

\textbf{All the projects mentioned above are on my GitHub}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Python > Bash, Java, Rust, Scala, Latex
  \item Platform: Linux
  \item Development: Linux Programming, Embedded Development.
  \item Learning : Rust, APUE
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize}, Award on China Undergraduate Mathematical Contest in Modeling.}{Nov. 2020}
\datedline{\textit{H Prize} Award on The Mathematical Contest in Modeling.}{Jun. 2020}
\datedline{\textit{Major Awaord} Scholarship of HeFei University of Technology.}{Oct. 2019}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/d0ot
  \item Languages: Mandarin - Native speaker, English - Intermediate(CET-6 528)
  \item Linux distro : Archlinx, I am a archlinux user, so I have mastered some linux commands.
  \item Editor : ViM, this is writen in latex with vimtex.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
